% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass[letterpaper]{www13-companion-accepted}
% \pdfpagewidth=8.5in
% \pdfpageheight=11in
% \usepackage[paperwidth=8.5in,paperheight=11in]{geometry}
\special{papersize=8.5in,11in}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{url}
% \usepackage{indentfirst}
\usepackage{cite}
\usepackage[T1]{fontenc}
\usepackage{color}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}

%\usepackage[normalem]{ulem}

\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{WWW 2013 Companion}{May 13-17, 2013, Rio de Janeiro, Brazil.}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

%\title{Temporal Evolution of Scientific Communities}
\title{The Role of Research Leaders on the \\ Evolution of Scientific Communities}
%\title{The Role of Leaders in the Dynamics of Scientific Communities}


\numberofauthors{3} %  in this sample file, there are a *total*
%
% 1st. author
%\alignauthor Bruno Leite Alves, Fabr\'icio Benevenuto, Alberto H. F. Laender\\
%       \affaddr{Departamento de Ci\^encia da Computa\c{c}\~ao}\\
%       \affaddr{Universidade Federal de Minas Gerais}\\
%       \affaddr{Belo Horizonte, Brazil}\\
%       \email{\{bruno.leite,Fabricio,Laender\}@dcc.ufmg.br}


\author{
% 1st. author
\alignauthor Bruno Leite Alves\\
% 2nd. author
\alignauthor Fabr\'icio Benevenuto\\
% 3rd. author
\alignauthor Alberto H. F. Laender
\and
\sharedaffiliation
\affaddr{Departamento de Ci\^encia da Computa\c{c}\~ao}\\
\affaddr{Universidade Federal de Minas Gerais}\\
\affaddr{Belo Horizonte, MG, Brazil}\\
\affaddr{\{bruno.leite, fabricio, laender\}@dcc.ufmg.br}
}


\maketitle
\begin{abstract}

\noindent
There have been considerable efforts in the literature towards understanding and modeling dynamic aspects of 
scientific communities. Despite the great interest, little is known about the role that different members play 
in the formation of the underlying network structure of such communities. In this paper, we provide a wide 
investigation of the roles that members of the core of scientific communities play in the collaboration network 
structure formation and evolution. To do that, we define a community core based on an individual metric, 
\textit{core score}, which is an h-index derived metric that captures both, the prolificness and the involvement
of researchers in a community. Our results provide a number of key observations related to community formation and 
evolving patterns. Particularly, we show that members of the community core work as bridges that connect smaller 
clustered research groups. Furthermore, these members are responsible for an increase in 
the average degree of the whole community underlying network and a decrease on the overall network assortativeness. 
More important, we note that variations on the members of the community core tend to be strongly correlated with 
variations on these metrics. We argue that our observations are important for shedding a light on the role of key 
members on community formation and structure.
\end{abstract}

% \vspace{-0.1cm}
\category{J.4.} {Computer Applications} Social and Behavioral Sciences
% \vspace{0.15cm}
\terms{Human Factors, Measurement.}
% \vspace{0.15cm}
\keywords{Scientific Communities, Core Community, Community Evolution.}
\vspace{1.4cm}
% \\ \\ \\ \\
\input{intro.tex}
\input{related.tex}
\input{data.tex}
\input{core.tex}
\input{analysis.tex}
\input{conclusion.tex}


\section{Acknowledgments}

This work was partially funded by InWeb - The Brazilian National Institute
of Science and Technology for the Web (grant MCT/CNPq 573871/2008-6), and
by the authors' individual grants from CNPq, CAPES e FAPEMIG.

\bibliographystyle{abbrv}
{
% \bibliography{short-references}  % sigproc.bib is the name of the Bibliography in this case

\begin{thebibliography}{10}

\bibitem{influence.correlation.kdd08}
A.~Anagnostopoulos, R.~Kumar, and M.~Mahdian.
\newblock Influence and correlation in social networks.
\newblock In {\em Proc. of KDD}, 2008.

\bibitem{fourdegrees_facebook}
L.~Backstrom, P.~Boldi, M.~Rosa, J.~Ugander, and S.~Vigna.
\newblock Four degrees of separation.
\newblock In {\em Proc. of ACM Web Science}, 2012.

\bibitem{Backstrom:2006}
L.~Backstrom, D.~Huttenlocher, J.~Kleinberg, and X.~Lan.
\newblock Group formation in large social networks: membership, growth, and
  evolution.
\newblock In {\em Proc. of KDD}, 2006.

\bibitem{icwsm10cha}
M.~Cha, H.~Haddadi, F.~Benevenuto, and K.~P. Gummadi.
\newblock {Measuring User Influence in Twitter: The Million Follower Fallacy}.
\newblock In {\em Proc. of ICWSM}, 2010.

\bibitem{Chakrabarti:2006:EC:1150402.1150467}
D.~Chakrabarti, R.~Kumar, and A.~Tomkins.
\newblock Evolutionary clustering.
\newblock In {\em Proc. of KDD}, 2006.

\bibitem{crandall.kdd08}
D.~Crandall, D.~Cosley, D.~Huttenlocher, J.~Kleinberg, and S.~Suri.
\newblock Feedback effects between similarity and social influence in online
  communities.
\newblock In {\em Proc. of KDD}, 2008.

\bibitem{Ducheneaut:2007}
N.~Ducheneaut, N.~Yee, E.~Nickell, and R.~J. Moore.
\newblock The life and death of online gaming communities: a look at guilds in
  world of warcraft.
\newblock In {\em Proc. of CHI}, 2007.

\bibitem{Hirsch:2005}
J.~E. Hirsch.
\newblock An index to quantify an individual's scientific research output.
\newblock {\em Proc. of the National Academy of Sciences},
  102(46):16569--16572, 2005.

\bibitem{citeulike:370723}
J.~Hopcroft, O.~Khan, B.~Kulis, and B.~Selman.
\newblock Tracking evolving communities in large linked networks.
\newblock {\em Proc. of the National Academy of Sciences}, 101(Suppl.
  1):5249--5253, April 2004.

\bibitem{Huang:2008}
J.~Huang, Z.~Zhuang, J.~Li, and C.~L. Giles.
\newblock Collaboration over time: characterizing and modeling network
  evolution.
\newblock In {\em Proc. of WSDM}, 2008.

\bibitem{Kempe05influentialnodes}
D.~Kempe, J.~Kleinberg, and \'{E}va Tardos.
\newblock Influential nodes in a diffusion model for social networks.
\newblock In {\em Proc. of ICALP}, 2005.

\bibitem{kempe03kdd}
D.~Kempe, J.~Kleinberg, and E.~Tardos.
\newblock Maximizing the spread of influence through a social network.
\newblock In {\em Proc. of KDD}, 2003.

\vfill\eject

\bibitem{Kleinberg@cacm2008}
J.~Kleinberg.
\newblock The convergence of social and technological networks.
\newblock {\em Commun. ACM}, 51(11):66--72, Nov. 2008.

\bibitem{Kumar:2006}
R.~Kumar, J.~Novak, and A.~Tomkins.
\newblock Structure and evolution of online social networks.
\newblock In {\em Proc. of KDD}, 2006.

\bibitem{Leskovec:2008}
J.~Leskovec, L.~Backstrom, R.~Kumar, and A.~Tomkins.
\newblock Microscopic evolution of social networks.
\newblock In {\em Proc. of KDD}, 2008.

\bibitem{Leskovec:2005}
J.~Leskovec, J.~Kleinberg, and C.~Faloutsos.
\newblock Graphs over time: densification laws, shrinking diameters and
  possible explanations.
\newblock In {\em Proc. of KDD}, 2005.

\bibitem{Leskovec@www2010}
J.~Leskovec, K.~J. Lang, and M.~Mahoney.
\newblock Empirical comparison of algorithms for network community detection.
\newblock In {\em Proc. of WWW}, 2010.

\bibitem{Ley:2009}
M.~Ley.
\newblock {DBLP}: some lessons learned.
\newblock {\em Proc. of VLDB Endownment}, 2(2):1493--1500, 2009.

\bibitem{mislove-2007-socialnetworks}
A.~Mislove, M.~Marcon, K.~P. Gummadi, P.~Druschel, and B.~Bhattacharjee.
\newblock {Measurement and Analysis of Online Social Networks}.
\newblock In {\em Proc. of IMC}, 2007.

\bibitem{Newman2003}
M.~Newman and J.~Park.
\newblock Why social networks are different from other types of networks.
\newblock {\em Phys. Rev. E}, 68, 2003.

\bibitem{Patil:2012}
A.~Patil, J.~Liu, B.~Price, H.~Sharara, and O.~Brdiczka.
\newblock Modeling destructive group dynamics in on-line gaming communities.
\newblock In {\em Proc. of ICWSM}, 2012.

\bibitem{Rogers.1962}
E.~M. Rogers.
\newblock {\em Diffusion of Innovations}.
\newblock 1962.

\bibitem{Sachan:2012}
M.~Sachan, D.~Contractor, T.~A. Faruquie, and L.~V. Subramaniam.
\newblock Using content and interactions for discovering communities in social
  networks.
\newblock In {\em Proc. of WWW}, 2012.

\bibitem{saez-trumper@kdd12}
D.~Saez-Trumper, G.~Comarela, V.~Almeida, R.~Baeza-Yates, and F.~Benevenuto.
\newblock Finding trendsetters in information networks.
\newblock In {\em Proc. of KDD}, 2012.

\bibitem{Seifi:2012:CCE:2187980.2188258}
M.~Seifi and J.-L. Guillaume.
\newblock Community cores in evolving networks.
\newblock In {\em Proc. of MSND}, 2012.

\bibitem{Viswanath:2009}
B.~Viswanath, A.~Mislove, M.~Cha, and K.~P. Gummadi.
\newblock On the evolution of user interaction in facebook.
\newblock In {\em Proc. of WOSN}, 2009.

\bibitem{accidental-influential}
D.~Watts and P.~Dodds.
\newblock Influentials, networks, and public opinion formation.
\newblock {\em Journal of Consumer Research}, 34(4):441--458, 2007.

\bibitem{Weng:2010:TFT:1718487.1718520}
J.~Weng, E.-P. Lim, J.~Jiang, and Q.~He.
\newblock Twitterrank: finding topic-sensitive influential twitterers.
\newblock In {\em Proc. of WSDM}, 2010.

\end{thebibliography}


}
\end{document}
