\section{Introduction}

Since its beginning, society has been organizing itself into communities, which are groups of people with common interests. Particularly, the proliferation of new communication
technologies based on the Internet has facilitated the rapid formation and growth of online communities. Communities exhibit a wide range of characteristics and serve a variety of
purposes, from small groups engaged in tightly niche topics such as a very specific scientific community, to millions of users linked by an interest such as a community related to
a sport team or fans of a celebrity. 

Often, individuals who are socially connected in a community tend to share interests and similarities. Although, there are many factors that might determine a community formation
and its growth, there are two main driven forces used to explain similarity in a community formation: influence and homophily. On one hand, influence posits that individuals change
to become more similar to their friends in the community. On the other hand, homophily postulates that individuals create social connections within a community precisely because
they are already similar. Recent efforts have provided quantitative evidences of both forces~\cite{icwsm10cha,crandall.kdd08,Backstrom:2006,influence.correlation.kdd08} and
existing theories~\cite{Rogers.1962,accidental-influential}, models~\cite{kempe03kdd,Kempe05influentialnodes}, and
approaches~\cite{saez-trumper@kdd12,Weng:2010:TFT:1718487.1718520} rely on identifying a group of influential individuals with the power to affect not only the underlying network
structure of a community, but also to interfere on the spread and flow of information within a community. 

In this paper, we take a different perspective and study a complementary problem. Here, we focus on studying the roles that scientific community leaders play and how they can impact intrinsic
evolving properties of research communities. When prolific research leaders decide to join or leave communities, they take with them resources,
experience, students and they possibly influence other authors to do the same, which makes scientific communities very suitable for this kind of study. We used data from DBLP to identify
scientific communities, represented by the main ACM SIGs conferences. Then, we propose a strategy to infer the community core, the leaders of a given scientific community in a
given period of time. Finally, we investigate how aspects of the core impact on the community structure. 

The study of the community core of scientific communities is of interest from two different perspectives.  The first is sociological, steemming from the necessity to understand how
segments of society evolve as well as to answer longstanding  questions related to the interaction among different types of participants. On the other hand, from a technological perspective,
understanding  these aspects is critical not only for link prediction as well as the designing better recommendation systems, but it is also a necessary step for viral marketing
strategies and social campaigns.  Such a study, however, has been difficult as essential components like human connections and a proper definition of leadership is hard to be
reproduced at a large scale within the confines of a research laboratory.

Our results show that (\red{TO DO}). 


The rest of this paper is organized as follows. Next section surveys related efforts. Then, Section 3 describes our strategy and dataset used to construct the connections around
scientific communities and analyzes the main evolving properties of this communities.  Section 4 describes our strategy to compute the community core and Section 5 investigate the
main properties of these sets of authors within their communities.  Finally, Section 6 concludes the paper and provides directions for future work. 




